Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-12 vesicle_code/docs/adhesion/adhesion.tex
minor changes at the bottom of page 10 by yny
starting shear

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
where $\chi$ is the shear rate.  The vesicles are placed on the $y$ axis
so that the background velocity drives the vesicles towards one another.
In the absence of adhesion, once the vesicles are sufficiently close,
they are deflected to opposite sides of the $y$ axis, pass one another,
and separate from one another.  However, in the presence of adhesion,
the vesicles can form a doublet for certain values of the adhesion
length scale $\delta$, Hamaker constant $\mathcal{H}$, shear rate
$\chi$, and reduced area $\Delta A$.  Figure~\ref{fig:doublet090} shows
snapshots two vesicles that have formed a doublet and the color coding
is the tension along the vesicle.  The two vesicles are
identical with reduced area is $\Delta A = 0.9$, the shear rate is $\chi
= 0.5$, the adhesion length scale is $\delta = 0.4$, and the Hamaker
constant is $\mathcal{H} = 0.7$.  Similar to the quiescent example, we
observe that the membrane tension in the contact region is negative in
the contact region indicating that the membrane is being compressed when
the adhesive force is strongest.  Once the vesicles have formed a
doublet, the vesicles rotate in tandem rather than performing the usual
tank-treading motion.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
where $\chi$ is the shear rate.  The vesicles are placed on the $y$ axis
so that the background velocity drives the vesicles towards one another.
In the absence of adhesion, once the vesicles are sufficiently close,
they are deflected to opposite sides of the $y$ axis, pass one another,
and then separate.  However, in the presence of adhesion, the vesicles
can form a doublet for certain values of the separation distance
$\delta$, Hamaker constant $\mathcal{H}$, shear rate $\chi$, and reduced
area $\Delta A$.  Figure~\ref{fig:doublet090} shows snapshots of two
vesicles that have formed a doublet and the color coding is the tension
along the vesicle.  The two vesicles are identical with reduced area
$\Delta A = 0.9$, shear rate $\chi = 0.5$, separation distance $\delta =
0.4$, and Hamaker constant $\mathcal{H} = 0.7$.  The vesicles in the
doublet move in tandem rather than performing the tank-treading motion
that is observed in the absence of adhesion.  Similar to the
quiescent example, the membrane tension is negative in the contact
region indicating that the membrane is being compressed when the
adhesive force is strongest.
